---
title: "Lab 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

``` {r}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)
library(tidyverse)
```

# Part A
1. Fit a model of the form lm(math ~ wave) for each student.

2. Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
``` {r}
benchmarks <- benchmarks %>%
  as_tibble() %>%
  mutate(wave = case_when(season == "Fall" ~ 0,
                          season == "Winter" ~ 1,
                          TRUE ~ 2))
by_student <- split(benchmarks, benchmarks$sid)

lms <- map(by_student, ~lm(math ~ wave, data = .x))

coefs <- map(lms, coef)

slopes <- map_dbl(coefs, 2)

data <- by_student %>% 
  map(~lm(math ~ wave, data = .x)) %>% 
  map(coef) %>% 
  map_dbl(2)

data <- tibble(id = names(data),
                   slope = data) %>% 
  drop_na()

ggplot(data, aes(x = slope)) +
  geom_histogram(fill = "cornflowerblue", color = "white") +
  geom_vline(aes(xintercept = mean(slope)))

```


# Part B
1. Use the sw_films list to identify how many characters were represented in each film.

2. Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.

``` {r}
library(repurrrsive)

map(sw_films, ~tibble(name = .x$title, characters = length(unique(.x$characters)))) %>% 
  bind_rows()

map(sw_species, ~tibble(species = .x$name, hair_color = .x$hair_colors)) %>% 
  bind_rows() %>% 
  filter(hair_color != "none" & hair_color != "n/a")
```

# Part C
1. Use {purrr} to write an API call to obtain data on the first five abilities (note, we’re only using the first five to make the calls go fast, but the code would be essentially equivalent for any number of abilities you wanted to query). Make sure you parse the JSON data to a list.

2. Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.
``` {r}
library(httr)
needs(glue)
ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
	content("parsed") 

abilities <- map(1:5, ~ GET(glue("https://pokeapi.co/api/v2/ability/{.x}")) %>%
	content("parsed"))

map_dfr(abilities, ~tibble(ability = .x$name,
                       pokemon = length(.x$pokemon))) 

```